### 2017-02-27 IROS17/theory2robAlgs.tex
Added algorithms and edited one more image.

\begin{algorithm}
\caption{WallFrictionMoveUp($r_1,r_2,g_1,g_2,L, moves$)}\label{alg:Wallup}
\begin{algorithmic}[1]
\scriptsize
\Require knowledge of current $(r_1,r_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
$(0,0)$ is bottom corner,
 $L$ is length of the walls. 
 The array \emph{moves} is the current moves up to the current position.
 Assume $r_1.x < r_2.x$ and $r_1.y \geq r_2.y$. If not, mirror the coordinate frame and swap the robots.
 $\epsilon $ is a small, nonzero, user-specified value.

\Ensure $(g_1, g_2) , (r_1, r_2)$ all at least $\epsilon$ distance from walls the goals and starting points have at least epsilon distance from each other.
\State $\Delta e = (g_2 - g_1)- (r_2- r_1)$
%\State $\Delta e_x = (g_2.x - g_1.x)- (r_2.x - r_1.x)$
\If $\Delta e = (0,0)$
\State 
\EndIf
\State Move $\left(-r_1.x , -\min \left(r_2.y , r_1.y+ \Delta e_y \right)+\epsilon \right)$ \Comment{Touch left wall}
%Second Move
%(-\min(|-r_2.x+ \Delta e_x|, r_2.x),
\State Move $ (r_2.x, |\sign(\Delta e_y)| \, \min(r_1.y - r_2.y + \Delta e_y-\epsilon,L-r_2.y-\epsilon)+ \epsilon)$
\Statex \Comment{Adjust  $y$}
%Third Move
\State Move $(\max(\epsilon, -\sign(r_2.y - r_1.y)\Delta e_x), -\min(r_1.y , r_2.y))$ 
\Statex \Comment{Touch bottom wall}
%Fourth Move
\State Move $(\sign(r_2.y - r_1.y)\Delta e_x , (|\sign(\Delta e_y)|-1) |r_2.y - r_1.y|)$ \Comment{Adjust $x$}
\If {$\Delta e_y \neq r_2.y - r_1.y$}
%Fifth Move
\If {$\Delta e_x \neq 0$}
\State Move $(\sign(r_2.y- r_1.y)\Delta e_x, |\sign(\Delta e_y)-1| |r_1.y-r_2.y|)$ \Comment{Touch right wall}
\Else
\State Move  $(|\sign(\Delta e_y -r_2.y+ r_1.y)| \epsilon, |\sign(\Delta e_y)-1| |r_1.y-r_2.y|)$ \Comment{Touch right wall}
\EndIf
%Sixth Move
\If {$\Delta e_x < 0$}
\State Move $(L - \max(r_1.x, r_2.x), \epsilon)$
\Else 
\State Move $(L - \max(r_1.x, r_2.x),\Delta e_y -\max(r_1.y, r_2.y)$ 
\Statex \Comment{Adjust $y$}
\EndIf
\EndIf
%Seventh Move
\State Move $(e_2.x - r_2.x, e_2.y - r_2.y)$ \Comment{Go to goal}
\end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
\caption{WallFrictionMoveUp($r_1,r_2,g_1,g_2,L, moves$)}\label{alg:Wallup}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of current $(r_1,r_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
$(0,0)$ is bottom corner,
 $L$ is length of the walls. 
 The array \emph{moves} is the current moves up to the current position.
 $m_1$ is the first move toward the wall or goal.
 $m_2$ is the second move adjusting $\Delta e$.
 Assume $r_1.x < r_2.x$ and $r_1.y \geq r_2.y$. If not, mirror the coordinate frame and swap the robots.
 $\epsilon $ is a small, nonzero, user-specified value.

\Ensure $(g_1, g_2) , (r_1, r_2)$ all at least $\epsilon$ distance from walls the goals and starting points have at least epsilon distance from each other.
\State $\Delta e = (g_2 - g_1)- (r_2- r_1)$
\State Admissible heuristic = $\max$(euclidian distance from goal)
%\State $\Delta e_x = (g_2.x - g_1.x)- (r_2.x - r_1.x)$
\If {$\Delta e = (0,0)$}
\State $m_1 = (g_2.x -  r_2.x, g_2.y - r_2.y)$
\State path $\gets$ path + $m_1$
\State Return (total distance of path, path)
\EndIf
\If {$r_2.x - r_1.x - 1 + 2 \epsilon \leq  \Delta g_x \leq  1 ~ \&\&~ r_2.y - r_1,y \leq \Delta g_y \leq  0$} %\Comment{Reachable region}
\State $m_1 = (\frac{1-r_1.y}{2-g_1.y-r_1.y} g_1.x -r_1.x, 1-r_1.y)$
\If {$r_2.x + m_1.x >L$}
\State $m_1.x = 1- r_2.x$
\EndIf
\If {$r_2.x + m_1.x <0$}
\State $m_1.x = -r_2.x$
\EndIf
\Else 
\State $m_1 = (0, 1-r_1.y)$
\State Adjust $\Delta g_x$ and $\Delta g_y$ %\Comment{To go to the nearest $\Delta g_x$ and $\Delta g_y$}
%\State $\Delta g_x = r_2.x - r_1.x - 1 + 2 \epsilon
\EndIf
\State path $\gets$ path + $m_1$
\State $r_1 = r_1 + m_1$ and $r_2 = r_2 + m_1$
\State $m_2 = (\Delta g_x - (r_2.x- r_1.x), \Delta g_y - (r_2.y-r_1.y))$
\If {Robots on each other or on the wall}
\State Add $\pm \epsilon$ to $m_2.x$
\EndIf
\State path $\gets$ path + $m_2$
%\State  $r_2 = r_2 + m_2$
\State Unmirror if necessary
\State Return(total distance of path + Admissible heuristic, path)
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{DynamicOptimalSolutionFinder($r_1,r_2,g_1,g_2,L$)}\label{alg:Wallup}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of current $(r_1,r_2)$ and goal $(g_1,g_2)$ positions of  two robots. 
$(0,0)$ is bottom corner,
 $L$ is length of the walls. 
 $OptimalPathList$ is a List containing all the paths sorted by their total distance. 
\State Pop the first element in OptimalPathList
\While {We have not reached the goal in the first element}
\State Call Alg. \ref{alg:Wallup} for all the four walls.
\State Add the results to OptimalPathList
\State Sort OptimalPathList
\EndWhile
\State Return(path)
\end{algorithmic}
\end{algorithm}
